The Morality of Arbitrage

### 2017-06-15 Draft/draft2.tex

Coherence in de Finetti's definition of probability is the counterpart
of the modern theory of no-arbitrage in finance.\footnote{See
  \citet{PressaccoZiani2010}.} Interestingly, de Finetti took a very
operational and economic approach to eliciting subjective probabilities.

The axioms of probability which characterize any theory of probability
arise logically from the condition that subjective probabilities
function as prices obeying coherency (i.e.~the arbitrage free
conditions).

Looking at problems of uncertainty as situations in which various
contingent claims are traded is the key insight offered by the
state-preference theory.

The dictionary definition of a Dutch book is the following:

>>>>

For de Finetti probability represents the subjective beliefs of the
agent. As \citet{Nau2001} explains: ``probability does not exist
\emph{objectively}, independently of the human mind. {[}P{]}robability
\ldots{} is a rate at which an individual is willing to \emph{bet on}
the occurence of an event. Betting rates are the primitive measurements
that reveal \emph{your} probabilities or \emph{someone else's}
probabilities, which are the only probabilities that really exist.'' de
Finettie tool a very operational view of eliciting probabilities. In his
theory, ``bets are for money, so your probability of an event is
effectively the \emph{price} that you are willing to pay for a lottery
ticket that yields \(1\) unit of money if the event occurs and nothing
otherwise.'' The reader trained in economics or finance will notice the
connection to the state-price theory of decision making under
uncertainty of \citet{Arrow1964} and \citet{Debreu1959}.\footnote{For a
  helpful review of state preference theory see Chapter 4 of
  \citet{CopelandWestonShastri}.} Coherence in de Finetti's definition
of probability is the counterpart of the modern theory of no-arbitrage
in finance.\footnote{See \citet{PressaccoZiani2010}.}

The axioms of probability which characterize any valid theory of
probability arise logically from the condition that subjective
probabilities function as prices obeying coherency (i.e.~the arbitrage
free conditions). Looking at problems of uncertainty as situations in
which various contingent claims are traded is the key insight offered by
the state-preference theory. ACT differs from the Arrow-Debreu setting
in that probabilities and utilities are non-separable, and only de
Finetti's \emph{previsions} are observable. In the modern parlance of
financial economics these are \emph{risk-neutral probabilities} (the
product of state-dependent subjective probabilities and utilities). ACT
relaxes the stance of methogological individualism of the neoclassical
trading. Rationality characterizes a market-level phenomenon rather than
individual behavior. Agents learn to be rational by adopting the
market's risk-neutral density as their prior through the market exchange
process. The connection to the information process in the Hayekian
setting becomes clear: prices convey information and represent agents'
subjective beliefs.

With this discussion of subjective probability and ACT as background we
can now discuss the Dutch Book Theorem. The dictionary definition of a
Dutch book is the following:
